Verifying Demonstrations

### 2018-05-25 paper/intro.tex
quick edits

\emph{Context.} Consider the following illustrative scenario.
Alice is an activist that organizes a protest in some location(s) against the 
current regime leader Grace.
On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Grace is an autocrat who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Grace.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.

Historically, there are many examples of protests in which the count estimated by police and that by the organizers 
differ significantly, sometimes in the order of hundreds of thousands.
The difference is actually quite natural as both parties have different objectives.
More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
Among the numerous recent examples in which it is difficult to establish the actual number of participants, we can cite the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.

@@

\seb{to do complete the contributions}
\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
Additionally, this verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfils all the requirements for modern \ac{DB} protocols, 
including \ac{DBDH} (which was an attach against Brands-Chaum).
More importantly, it is public key (\ie handles malicious, impersonating 
verifiers), fulfils \ac{DBTF} and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the 
\ac{ZKPK} used in anonymous credentials and thus we are, to the best of our 
knowledge, the first to provide \ac{DB} anonymous credentials.

\emph{Limitations and assumptions.} Some of the assumptions that are required 
for implementing our proposition are not yet realized (see \cref{assumptions} 
for more detailed descriptions). In particular, not all (or even many) 
protesters, especially in countries with oppressive regimes, currently possess 
smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
\seb{maybe to prevent the above issue, we could require the individual to 
  generate his secret key and only use the authority to obtain a certification 
  on his public key (in the spirit of blind signature)}
\daniel{That's what we currently do.
  But the government is the authority, so the government can generate and 
  certify its own keys.}
In this case, it does not make sense to verify any pro-government protests in 
which Grace's authoritarian regime wants to demonstrate its wide support, 
\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not 
feasible within a meaningful range of distance needed for our scenario.
They lack the required hardware to do the distance bounding fast enough.

>>>>

\emph{Context.} Consider the following illustrative scenario.
Alice is an activist that organizes a protest in some location(s) against the 
current government, represented by Grace.
On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Grace.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.

Historically, there are many examples of protests in which the count estimated by police and that by the organizers 
differ significantly, sometimes in the order of hundreds of thousands.
Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.

@@

\seb{to do complete the contributions}
\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfils all the requirements for modern \ac{DB} protocols, 
including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public key (\ie handles malicious, impersonating 
verifiers), fulfils \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the 
\ac{ZKPK} used in anonymous credentials and thus we are, to the best of our 
knowledge, the first to provide \ac{DB} anonymous credentials.

\emph{Limitations and assumptions.} Some of the assumptions that are required 
for implementing our proposition are not yet realized (briefly, use of smartphones, unique identities, distance bounding - see \cref{assumptions} 
for more detailed descriptions). In particular, not all (or even many) 
protesters, especially in countries with oppressive regimes, currently possess 
smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
\seb{maybe to prevent the above issue, we could require the individual to 
  generate his secret key and only use the authority to obtain a certification 
  on his public key (in the spirit of blind signature)}
\daniel{That's what we currently do.
  But the government is the authority, so the government can generate and 
  certify its own keys.}
In this case, it does not make sense to verify any pro-government protests in 
which Grace's authoritarian regime wants to demonstrate its wide support, 
\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not 
feasible within a meaningful range of distance needed for our scenario.
They lack the required hardware to do the distance bounding fast enough.
